### 2022-11-05 doc/src/MSLevel.tex
Fix WFI
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

>>>>

%-----------------------------------------------------------------------
\section{WFI (Wait for Interrupt) instruction}

The {\RISCV} Privileged Architecture specifies that
instruction WFI (Wait for Interrupt) may suspend execution
at a hart until an interrupt is pending for the hart.
The Advanced Interrupt Architecture (AIA) redefines
when execution must resume following a WFI.

According to the {\RISCV} Privileged Architecture, instruction
execution must resume from a WFI whenever any interrupt
is both pending and enabled in CSRs \z{mip} and \z{mie},
ignoring any delegation indicated by \z{mideleg}.
With the AIA, this succinct rule is no longer appropriate,
due to the mechanisms the AIA adds for virtual interrupts.
Instead, execution must resume from a WFI whenever
an interrupt is pending at any privilege level
(regardless of whether the interrupt privilege level is
higher or lower than the hart's current privilege mode).

An interrupt is pending at machine level
if register \z{mtopi} is not zero.
If \mbox{S-mode} is implemented, an interrupt is
pending at supervisor level if \z{stopi} is not zero.
And if the hypervisor extension is implemented, an interrupt is pending
at VS level if \z{vstopi} (Section~\ref{sec:vstopi}) is not zero.

\begin{commentary}
The AIA's rule for WFI gives the same behavior as the Privileged
Architecture's rule when\/ \z{mvien} =~0 and, if the hypervisor
extension is implemented, also \z{hvien} =~0 and\/ \z{hvictl}.VTI =~0,
thus disabling all virtual interrupts not visible in\/ \z{mip}.
(The AIA's hypervisor registers are covered in the next chapter,
``Interrupts for Virtual Machines (VS Level)''.)
\end{commentary}
